DAG test

### 2022-11-13 DAG.Rmd
Commit

lf_test ~ theta_00 + theta_01 * TSLAG(ur_ds,1)

,TSDELTALOG(shock_kuld) ~  a_5* log(TSLAG(komp_r,1)) + a_6* log(TSLAG(shock_kuld,1)) + a_7*d_2013q1

,max_dp ~ TSLAG(max_dp,4)+ (stat_reg+stat_tilpas)*TSLAG(max_dp,4)

@@

,LOG(pg) ~ 0.840852289293*LOG(pc) - 0.0401650251402 +
pg_adj

,LOG(p_bd) ~ 0.988897636487*LOG(pc) + 0.0286611434831 +
p_bd_adj

,LOG(p_equip) ~ 0.304376220161*LOG(pc) + 0.0160136953595
+ p_equip_adj

,LOG(px) ~ 0.638216896739*LOG(pc) - 0.012650117362 +
px_adj

@@

,TSDELTALOG(pconk_ds) ~   C_2*TSLAG(LOG(pconk_ds),1) + C_3*TSLAG(LOG(yd1_hk_ds),1) + C_4*LOG(TSLAG(yd2a_hk_ds,1) + TSLAG(yd2b_hk,1)) + C_5*TSLAG(LOG(fnw_hk),2) + C_6*TSDELTALOG(TSLAG(pconk_ds,2)) + C_7*TSDELTALOG(TSLAG(pconk_ds,3)) + C_8*TSDELTALOG(yd1_hk_ds)  + C_9*TSDELTALOG(yd2a_hk_ds + yd2b_hk) + C_10*d_2008q4 + C_11*d_2018q2 + C_12*d_2020q1 + C_13* time

@@

,LOG(i_bd_h_k_ds) ~ P_620 + 
P_621*TSDELTALOG(TSLAG(i_bd_h_k_ds,1)/TSLAG(bd_h_k,2))+ 
P_622*TSDELTALOG(TSLAG(i_bd_h_k_ds,3)/TSLAG(bd_h_k,4))+ 
P_623*TSDELTALOG(TSLAG(p_bd,1)/TSLAG(pi_1,1)) + 
P_624*TSDELTALOG(TSLAG(p_bd,2)/TSLAG(pi_1,2)) + 
P_625*TSDELTALOG(TSLAG(yd_hk_ds,2)/TSLAG(bd_h_k,3))+ 
P_626*TSDELTALOG(TSLAG(-l_h,1)/TSLAG(bd_h,2)) + 
P_627*LOG(TSLAG(i_bd_h_k_ds,1)/TSLAG(bd_h_k,2)) + 
P_628*LOG(TSLAG(yd_hk_ds,1)/TSLAG(bd_h_k,2)) + 
P_629*LOG(TSLAG(p_bd,1)/TSLAG(pi_1,1)) +
P_630*LOG(TSLAG(-l_h,1)/TSLAG(bd_h,2)) + 
P_631*d_2006q4 + 
P_632*d_2014q4 + 
alpha_1*LOG(TSLAG(bd_h_k,1)) + 
alpha_2* TSLAG(LOG(i_bd_h_k_ds),1) + 
alpha_3* TSLAG(-LOG(bd_h_k),2)

@@

,TSDELTALOG(nben_h_rest) ~ P_671 + P_672*TSDELTALOG(zaland_jesper) + P_673*TSDELTA(unemp) + P_674*TSDELTA(TSLAG(unemp,1)) +   P_675*LOG(TSLAG(nben_h_rest,1)) + P_676*TSLAG(unemp,1) + P_677*LOG(TSLAG(zaland_jesper,1))

@@

,TSDELTA(l_h_tr_ratio) ~ p_646 
+ p_641*TSDELTA(TSLAG(l_h_tr_ratio,2))
+ p_642*TSDELTA(iloan) 
+ p_643*TSDELTALOG(TSLAG(i_bd_h_k_ds,3)/TSLAG(yd_hk_ds,3)) 
+ p_644* TSLAG(l_h_tr_ratio,1) 
+ p_645*LOG(TSLAG(-l_h,2)/(TSLAG(yd_hk_ds,2)*TSLAG(pc,2)))
+ p_647*d_2007q34 
+ p_648*time

@@

,TSDELTA(eq_h_ratio) ~  p_770  
+ p_771* TSDELTA(TSLAG(ibd,1))
+ p_772* TSDELTA(TSLAG(ratio_in_eq_h,1))
+ p_773* TSLAG(eq_h_ratio,1)
+ p_774* TSLAG(ibd,1) 
+ p_775* TSLAG(ratio_in_eq_h,2)

@@

,TSDELTALOG(d8_h) ~ p_701*TSDELTALOG(TSLAG(d8_h,1)) + p_702*TSDELTALOG(w_h_r) + p_703*TSDELTALOG(TSLAG(old_age_ratio,1)) + p_704*LOG(TSLAG(d8_h,1)) + p_705*LOG(TSLAG(w_h_r,1)) + p_706*LOG(TSLAG(old_age_ratio,1)) + p_707*d_2014q3

@@

,TSDELTA(bd_h_k) ~ i_bd_h_k - TSLAG(bd_h_k,1) * delta_bd_h

,TSDELTA(equip_h_k) ~ i_equip_h_k - TSLAG(equip_h_k,1) * delta_equip_h

,TSDELTA(bd_h) ~ i_bd_h + TSLAG(bd_h_k,1) * (1-delta_bd_h)*TSDELTA(p_bd) - TSLAG(bd_h_k,1) * delta_bd_h * p_bd

,TSDELTA(equip_h) ~ i_equip_h + TSLAG(equip_h_k,1) * (1-delta_equip_h)*TSDELTA(p_equip) - TSLAG(equip_h_k,1) * delta_equip_h * p_equip

@@

,TSDELTALOG(xk_ds) ~  p_652*TSDELTALOG(TSLAG(gdp_tp,4)) + p_653*TSDELTALOG(rer) + p_654*LOG(TSLAG(xk_ds,1)) + p_655*LOG(TSLAG(gdp_tp,1)) + p_656*LOG(TSLAG(rer,2)) + p_657*d_2008q2 + p_658*d_2018q1 + p_659*d_2019q3 + p_660* time

@@

,TSDELTALOG(mk_ds) ~ p_661 + p_662*TSDELTALOG(TSLAG(mk_ds,2)) + p_663*TSDELTALOG(TSLAG(rer,1)) + p_664*TSDELTALOG(TSLAG(rer,3)) + p_665*TSDELTALOG(yk_ds) + p_666*LOG(TSLAG(mk_ds,1)) + p_667*LOG(TSLAG(yk_ds,1)) + p_668*d_2009q1 + p_669*d_2009q4

@@

,LOG(i_bd_nfc_k_ds_used ~ p_800 + 
p_801*TSDELTALOG(TSLAG(i_bd_nfc_k_ds,1)/TSLAG(bd_nfc_k,2)) + 
p_802*TSDELTALOG(ps_ds) + 
p_803*TSDELTALOG(u_ds) + 
p_804* LOG(TSLAG(i_bd_nfc_k_ds,1)/TSLAG(bd_nfc_k,2)) + 
p_805 * LOG(TSLAG(ps_ds,1)) + 
p_806 * LOG(TSLAG(u_ds,1)) + 
p_807 * TSDELTALOG(tobinq) +
p_808 * LOG(TSLAG(tobinq,1)) +
alpha_1*TSLAG(LOG(i_bd_nfc_k_ds),1) + 
alpha_2*TSLAG(LOG(bd_nfc_k),1) + 
alpha_3*TSLAG(-LOG(bd_nfc_k),2)

@@

,fab ~ (fnl_row)

@@

,emp_old ~ p_250 * (yk/prodk)

,emp_sens ~ p_251 * (yk/prodk)

,emp ~ emp_old

@@

,wage_ds_t~ wage_ds*(1+inflation_t)

@@

,max_gap ~ 0.42

@@

,inflation_t ~ inflation_tt

@@

,prod_ds_shock ~  pr_1* TSDELTALOG(wage_ds) +
pr_2* TSDELTALOG(TSLAG(y_ds,4)) +
pr_3* TSDELTALOG(y_ds) + 
pr_4* TSDELTALOG(TSLAG(wage_ds,1)) +
pr_8* LOG(TSLAG(y_ds,2))+
pr_9* LOG(TSLAG(dp_person,2))+
pr_10* LOG(TSLAG(prod_ds_shock,1))+
pr_11* LOG(TSLAG(wage_ds,2))

,prod_ds_sens ~  pr_1* TSDELTALOG(wage_ds) +
pr_2* TSDELTALOG(TSLAG(y_ds,4)) +
pr_3* TSDELTALOG(y_ds) + 
pr_4* TSDELTALOG(TSLAG(wage_ds,1)) +
pr_8* LOG(TSLAG(y_ds,2))+
pr_9* LOG(TSLAG(dp_person,2))+
pr_10* LOG(TSLAG(prod_ds_sens,1))+
pr_11* LOG(TSLAG(wage_ds,2))

@@

,i_bd_nfc_k_ds~ i_bd_nfc_k_ds_used

@@

,part1 ~ beta_0 + beta_1*TSDELTALOG(TSLAG(part1,2)) + beta_2*TSDELTALOG(TSLAG(part1,3))  +beta_3*TSDELTALOG(TSLAG(kont_h_ratio,1)) +beta_4*TSDELTALOG(rw_ds)  +beta_5*TSDELTALOG(TSLAG(rw_ds,2)) +beta_6*TSDELTALOG(TSLAG(rw_ds,3))  + beta_8*LOG(TSLAG(part1,1))  + beta_9*log(TSLAG(rw_ds,1)) + beta_10*log(TSLAG(kont_h_ratio,1)) + beta_11*TSLAG(ur_ds,1)

,kont_h_ratio ~ kont_h / dp_person
)

@@

```{r}
eq1= sfcr_set(

  part1 ~ beta_0 + beta_1*TSDEpart1,2 + beta_2*TSDELTALOG(TSLAG(part1,3))  +beta_3*TSDELTALOG(TSLAG(kont_h_ratio,1)) +beta_4*TSDELTALOG(rw_ds)  +beta_5*TSDELTALOG(TSLAG(rw_ds,2)) +beta_6*TSDELTALOG(TSLAG(rw_ds,3))  + beta_8*LOG(TSLAG(part1,1))  + beta_9*log(TSLAG(rw_ds,1)) + beta_10*log(TSLAG(kont_h_ratio,1)) + beta_11*TSLAG(ur_ds,1),

  ur_ds ~ rw_ds,

  rw_ds~ part1

)
```

```{r, fig.width=15, fig.height=7}
sfcr_dag_cycles_plot(eq1, size = 4)
```

>>>>

max_dp ~ TSLAG(max_dp,4)+ (stat_reg+stat_tilpas)*TSLAG(max_dp,4)

@@

,pg ~ 0.840852289293*LOG(pc) - 0.0401650251402 +
pg_adj

,p_bd ~ 0.988897636487*LOG(pc) + 0.0286611434831 +
p_bd_adj

,p_equip ~ 0.304376220161*LOG(pc) + 0.0160136953595
+ p_equip_adj

,px ~ 0.638216896739*LOG(pc) - 0.012650117362 +
px_adj

@@

,pconk_ds ~   C_2*TSLAG(LOG(pconk_ds),1) + C_3*TSLAG(LOG(yd1_hk_ds),1) + C_4*LOG(TSLAG(yd2a_hk_ds,1) + TSLAG(yd2b_hk,1)) + C_5*TSLAG(LOG(fnw_hk),2) + C_6*TSDELTALOG(TSLAG(pconk_ds,2)) + C_7*TSDELTALOG(TSLAG(pconk_ds,3)) + C_8*TSDELTALOG(yd1_hk_ds)  + C_9*TSDELTALOG(yd2a_hk_ds + yd2b_hk) + C_10*d_2008q4 + C_11*d_2018q2 + C_12*d_2020q1 + C_13* time

@@

,i_bd_h_k_ds ~ P_620 + 
P_621*TSDELTALOG(TSLAG(i_bd_h_k_ds,1)/TSLAG(bd_h_k,2))+ 
P_622*TSDELTALOG(TSLAG(i_bd_h_k_ds,3)/TSLAG(bd_h_k,4))+ 
P_623*TSDELTALOG(TSLAG(p_bd,1)/TSLAG(pi_1,1)) + 
P_624*TSDELTALOG(TSLAG(p_bd,2)/TSLAG(pi_1,2)) + 
P_625*TSDELTALOG(TSLAG(yd_hk_ds,2)/TSLAG(bd_h_k,3))+ 
P_626*TSDELTALOG(TSLAG(-l_h,1)/TSLAG(bd_h,2)) + 
P_627*LOG(TSLAG(i_bd_h_k_ds,1)/TSLAG(bd_h_k,2)) + 
P_628*LOG(TSLAG(yd_hk_ds,1)/TSLAG(bd_h_k,2)) + 
P_629*LOG(TSLAG(p_bd,1)/TSLAG(pi_1,1)) +
P_630*LOG(TSLAG(-l_h,1)/TSLAG(bd_h,2)) + 
P_631*d_2006q4 + 
P_632*d_2014q4 + 
alpha_1*LOG(TSLAG(bd_h_k,1)) + 
alpha_2* TSLAG(LOG(i_bd_h_k_ds),1) + 
alpha_3* TSLAG(-LOG(bd_h_k),2)

@@

,nben_h_rest ~ P_671 + P_672*TSDELTALOG(zaland_jesper) + P_673*TSDELTA(unemp) + P_674*TSDELTA(TSLAG(unemp,1)) +   P_675*LOG(TSLAG(nben_h_rest,1)) + P_676*TSLAG(unemp,1) + P_677*LOG(TSLAG(zaland_jesper,1))

@@

,l_h_tr_ratio ~ p_646 
+ p_641*TSDELTA(TSLAG(l_h_tr_ratio,2))
+ p_642*TSDELTA(iloan) 
+ p_643*TSDELTALOG(TSLAG(i_bd_h_k_ds,3)/TSLAG(yd_hk_ds,3)) 
+ p_644* TSLAG(l_h_tr_ratio,1) 
+ p_645*LOG(TSLAG(-l_h,2)/(TSLAG(yd_hk_ds,2)*TSLAG(pc,2)))
+ p_647*d_2007q34 
+ p_648*time

@@

,eq_h_ratio ~  p_770  
+ p_771* TSDELTA(TSLAG(ibd,1))
+ p_772* TSDELTA(TSLAG(ratio_in_eq_h,1))
+ p_773* TSLAG(eq_h_ratio,1)
+ p_774* TSLAG(ibd,1) 
+ p_775* TSLAG(ratio_in_eq_h,2)

@@

,d8_h ~ p_701*TSDELTALOG(TSLAG(d8_h,1)) + p_702*TSDELTALOG(w_h_r) + p_703*TSDELTALOG(TSLAG(old_age_ratio,1)) + p_704*LOG(TSLAG(d8_h,1)) + p_705*LOG(TSLAG(w_h_r,1)) + p_706*LOG(TSLAG(old_age_ratio,1)) + p_707*d_2014q3

@@

,bd_h_k ~ i_bd_h_k - TSLAG(bd_h_k,1) * delta_bd_h

,equip_h_k ~ i_equip_h_k - TSLAG(equip_h_k,1) * delta_equip_h

,bd_h ~ i_bd_h + TSLAG(bd_h_k,1) * (1-delta_bd_h)*TSDELTA(p_bd) - TSLAG(bd_h_k,1) * delta_bd_h * p_bd

,equip_h ~ i_equip_h + TSLAG(equip_h_k,1) * (1-delta_equip_h)*TSDELTA(p_equip) - TSLAG(equip_h_k,1) * delta_equip_h * p_equip

@@

,xk_ds ~  p_652*TSDELTALOG(TSLAG(gdp_tp,4)) + p_653*TSDELTALOG(rer) + p_654*LOG(TSLAG(xk_ds,1)) + p_655*LOG(TSLAG(gdp_tp,1)) + p_656*LOG(TSLAG(rer,2)) + p_657*d_2008q2 + p_658*d_2018q1 + p_659*d_2019q3 + p_660* time

@@

,mk_ds ~ p_661 + p_662*TSDELTALOG(TSLAG(mk_ds,2)) + p_663*TSDELTALOG(TSLAG(rer,1)) + p_664*TSDELTALOG(TSLAG(rer,3)) + p_665*TSDELTALOG(yk_ds) + p_666*LOG(TSLAG(mk_ds,1)) + p_667*LOG(TSLAG(yk_ds,1)) + p_668*d_2009q1 + p_669*d_2009q4

@@

,i_bd_nfc_k_ds_used ~ p_800 + 
p_801*TSDELTALOG(TSLAG(i_bd_nfc_k_ds,1)/TSLAG(bd_nfc_k,2)) + 
p_802*TSDELTALOG(ps_ds) + 
p_803*TSDELTALOG(u_ds) + 
p_804* LOG(TSLAG(i_bd_nfc_k_ds,1)/TSLAG(bd_nfc_k,2)) + 
p_805 * LOG(TSLAG(ps_ds,1)) + 
p_806 * LOG(TSLAG(u_ds,1)) + 
p_807 * TSDELTALOG(tobinq) +
p_808 * LOG(TSLAG(tobinq,1)) +
alpha_1*TSLAG(LOG(i_bd_nfc_k_ds),1) + 
alpha_2*TSLAG(LOG(bd_nfc_k),1) + 
alpha_3*TSLAG(-LOG(bd_nfc_k),2)

@@

,fab ~ fnl_row

@@

,emp ~ p_250 * (yk/prodk)

@@

,wage_ds_t~ wage_ds*(1+inflation)

@@

@@

@@

@@

@@

)

@@

# plot

```{r, fig.width=15, fig.height=7}
sfcr_dag_cycles_plot(eq)
```

# Table

```{r}
tb_graph=sfcr_dag_cycles(eq)
```
